Mergeable Types

### 2017-02-28 paper/intro.tex
edits

\noindent The remainder of the paper is organized as follows.  We present the
\name\ programming model informally in the next section.
Sec.~\ref{sec:mergeable_types} develops a series of examples that
illustrate how merge operations can be defined and used.
Sec.~\ref{sec:formalization} defines an operational semantics, and
formalizes our intuition of a mergeable type in terms of morphisms over
datatype operations.  We also present soundness (consistency) and
progress guarantees enjoyed by the
semantics. Sec.~\ref{sec:system-model} considers an instantiation of
the model suitable for distributed environments with network
partitions and failures.  Implementation details describing how we
incorporate mergeable types into OCaml are presented in
Sec.~\ref{sec:impl}.  Experimental results and benchmarks are given in
Sec.~\ref{sec:evaluation}.  Secs.~\ref{sec:related}
and~\ref{sec:conclusions} describes related work and conclusions.

>>>>

\noindent The remainder of the paper is organized as follows.  We present the
\name\ programming model informally in the next section.
Sec.~\ref{sec:mergeable_types} develops a series of examples that illustrate
how merge operations can be defined and used. Sec.~\ref{sec:formalization}
defines an operational semantics, and formalizes our intuition of a mergeable
type in terms of morphisms over datatype operations.  We also present soundness
(consistency) and progress guarantees enjoyed by the semantics.
Sec.~\ref{sec:implementation} presents an instantiation of the model suitable
for highly-available distributed environments with network partitions and
failures. Experimental results and benchmarks are given in
Sec.~\ref{sec:evaluation}.  Secs.~\ref{sec:related} and~\ref{sec:conclusions}
describes related work and conclusions.
